---
title: "R Notebook"
output: html_notebook
---

```{r}
library(here)
library(groundhog)
pkgs <- c("ggplot2","optimx","igraph","compiler","doParallel","parallel","lmerTest","lme4")
library(Hmisc)
groundhog.day <- "2022-07-25"
groundhog.library(pkgs, groundhog.day)
library(here)
here::i_am("./Recovery/fMRIparameterfeedRecovery.Rmd")
setwd("~/Google Drive/Volumes/")
allCents <- read.csv("./Research Project/Trait Network_Behaviral/generating network/output/allPosCents.csv")
fullDf <- read.csv("./Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/fullDf.csv")
posDf <- read.csv("./Research Project/Trait Network_Behaviral/generating network/output/adjacencyMatrix_p.csv")
posMat <- as.matrix(posDf)
posGraph <- graph.adjacency(posMat)

names(allCents)[colnames(allCents)=="trait"] <- "Trait"
fullDf <- merge(fullDf, allCents, by="Trait")
```

```{r}
setwd("~/Google Drive/Volumes/Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/RL Models/")
source("graphMix.R")
cGraphMix <- cmpfun(graphMix)
source(here("Recovery","graphMixParamRecov.R"))
cGraphMixParamRecov <- cmpfun(graphMixParamRecov)
cOptimx <- cmpfun(optimx)
  zScore <- function(input, m, s){
    output<-(input - m)/s
    return(output)
  }
  zScore <- cmpfun(zScore)
```

```{r}
setwd("~/Google Drive/Volumes/Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/output/")
AsymLR.ParamDf <- read.csv("GraphMix.ParamDf.csv")
tBt_Df <- read.csv("trialBytrial.Df.csv")
```

# import workspace since it takes a long time to re-run

```{r}
#load("~/Google Drive/Volumes/Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/fMRIparameterRecover_2021_08_05_JE.RData")
```


```{r}
uIds<-unique(fullDf$subID)
uIds<-uIds[!is.na(uIds)]
```

# Generate cormat for original parameters

```{r}
cormat <- round(cor(AsymLR.ParamDf[2:4]),2)
library(reshape2)
melted_cormat <- melt(cormat)
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)

# Create a ggheatmap
ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 25, hjust = 1), axis.text.y = element_text( 
    size = 25) )+
 coord_fixed()

greekLab <- c(expression(alpha[p]), expression(alpha[n]), expression(phi) )

OrigOrigHeatMap <- ggheatmap + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_text(size=18, face="bold"),
  axis.title.y = element_text(size=18, face="bold"),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(0.48, 0.7),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5)) + xlab("Original") + ylab("Original") +
  scale_x_discrete(
        labels=greekLab)  +
  scale_y_discrete(
        labels=greekLab)
OrigOrigHeatMap
```

# Generate simulated parameters

```{r}
set.seed(52)

iter<- 500

posLRseq<-seq(from = quantile(AsymLR.ParamDf$posLR)[2], to = quantile(AsymLR.ParamDf$posLR)[4], length.out = 5)
negLRseq<-seq(from = quantile(AsymLR.ParamDf$negLR)[2], to = quantile(AsymLR.ParamDf$negLR)[4], length.out = 5)
mixseq <-seq(from = quantile(AsymLR.ParamDf$mix)[2], to = quantile(AsymLR.ParamDf$mix)[4], length.out = 5)

posLRnoised <- c()
negLRnoised <- c()
mixnoised <- c()

bounded <- function(param){
  if(param>=1){
    param <- 1
  } else if(param<=0){
    param <- 0
  }
}
boundedRnorm <- function(n, mean = 0, sd = 1, lb = -1, ub = 1){
  output <- rnorm(n, mean, sd)
  if(n > 1){
    while(any(output < 0) | any(output > 1)){
    inds <- which(output > 1 | output < 0)
    output[inds] <- rnorm(length(inds), mean, sd)
  }
  } else if (n == 1){
    while(output < 0 | output > 1){
    output <- rnorm(n, mean, sd)
    }
  }
  return(output)
}

for(i in 1:5){
  for(k in 1:(iter/5)){
    
    #posLRnoised <- c(posLRnoised, bounded(rnorm(1, posLRseq[i], sd(AsymLR.ParamDf$posLR)/4 )) )
    posLRnoised <- c(posLRnoised, boundedRnorm( 1, posLRseq[i], sd(AsymLR.ParamDf$posLR)/4 ))
    #negLRnoised <- c(negLRnoised, bounded(rnorm(1, negLRseq[i], sd(AsymLR.ParamDf$negLR)/4 )) )
    negLRnoised <- c(negLRnoised, boundedRnorm( 1, negLRseq[i], sd(AsymLR.ParamDf$negLR)/4 ) )
    #mixnoised <- c(mixnoised, bounded(rnorm(1, mixseq[i], sd(AsymLR.ParamDf$mix)/4 )) )
    mixnoised <- c(mixnoised, boundedRnorm(1, mixseq[i], sd(AsymLR.ParamDf$mix)/4 ))

  }
}

posLRnoised[posLRnoised==0] = posLRnoised[posLRnoised==0] + abs(rnorm(length(posLRnoised[posLRnoised==0]),0,sd(AsymLR.ParamDf$posLR)/5 ))

negLRnoised[negLRnoised==0] = negLRnoised[negLRnoised==0] + abs(rnorm(length(negLRnoised[negLRnoised==0]),0,sd(AsymLR.ParamDf$negLR)/5 ))

mixnoised[mixnoised==0] = mixnoised[mixnoised==0] + abs(rnorm(length(mixnoised[mixnoised==0]),0,sd(AsymLR.ParamDf$mix)/5 ))

seqParams <- data.frame(posLR = sample(posLRnoised, iter, replace = F), negLR = sample(negLRnoised, iter, replace = F), mix = sample(mixnoised, iter, replace = F)
                        )

hist(seqParams$posLR, breaks =50)
hist(seqParams$negLR, breaks = 50)
hist(seqParams$mix, breaks = 50)
```
# Generate behavioral data from simulated parameters

```{r}
x<-c('trialNum', paste0('wpe',1:148) , paste0('ws',1:148), 'RPE','V_PE', 'S_PE', 'V_S', 'Value', 'SR', 'cluster', 'prob', 'clustType', 'Idx', 'valence', 'feedback','i')
simulated<-as.data.frame(matrix(ncol=length(x)))
names(simulated) <- x
simParams <- matrix(ncol=4)
set.seed(42)
for(i in 1:iter){
  
  sampParams<-c(seqParams$posLR[i], seqParams$negLR[i], seqParams$mix[i])
  curSim<-graphMixParamRecov(sampParams, type = "in", graph = posGraph)
  sampParams<-c(sampParams, i)
  curSim <- cbind(curSim, i)
  simulated<-rbind(simulated, curSim)
  simParams<-rbind(simParams, sampParams)
  
}
simulated<-simulated[2:nrow(simulated),1:ncol(simulated)]
simParams<-simParams[2:nrow(simParams),1:ncol(simParams)]

simulated<-as.data.frame(simulated)
simParams<-as.data.frame(simParams)
names(simParams) <- c("posLR","negLR","mix","simID")
names(simulated)[colnames(simulated)=="i"] <- "simID"
```
# OLS fits on simulated data

```{r}

  set.seed(132)
  simulated <- simulated[!is.na(simulated$SR),] # Remove missing responses; data will not fit with missing responses included
  simulated <- simulated[order(simulated$simID, simulated$trialNum),] # Sort by trials for trial-by-trial learning
  simIds <- unique(simulated$simID)
  x = c("simID", "posLR", "negLR", "mix", "LL", "k", "n", "BIC", "AIC")
  k = 3

  core<-detectCores()
  cl <- parallel::makeCluster(core-2, setup_strategy = "sequential")
  setDefaultCluster(cl=cl)
  registerDoParallel(cl)
  clusterExport(cl, list("cGraphMix"))
  clusterExport(cl, list("x"))
  clusterExport(cl, list("k"))
  clusterExport(cl, list("simulated"))
  
result<-foreach(i=simIds, .combine = rbind.data.frame, .export=c('cGraphMix', 'cOptimx', 'fullDf', 'x', 'k'), .packages = c("compiler", "optimx", "scales")) %dopar% {
  paramDf <- as.data.frame(matrix(ncol = length(x)))
  names(paramDf) <- x
  subDf <- subset(simulated, simID == i) # Subset participant data
  SSE <- function(param){ (sum((subDf$SR  - (cGraphMix(subDf$trialNum,subDf$Idx,subDf$feedback,4,posGraph,type="in",cue="single",param)$Value))^2)) } # Set objective function for SSE
  
  (output <- optimx(par = c(.04, .04, .5), method = c("L-BFGS-B"), fn = SSE, lower = c(0, 0, 0), upper = c(1,1,1))) # Set parameters for optimization
  paramDf$simID <- i
  paramDf$posLR <- output$p1
  paramDf$negLR <- output$p2
  paramDf$mix <- output$p3
  paramDf$k <- k
  paramDf$n <- nrow(subDf)
  paramDf$LL <- output$value
  paramDf$BIC <- nrow(subDf) * log(output$value/nrow(subDf)) + k * log(nrow(subDf)) # Compute BIC
  paramDf$AIC <- 2 * k + nrow(subDf) * log(output$value/nrow(subDf))
  paramDf
    
}
stopCluster(cl)
OLS_GraphMixRecov.ParamDf <- result

simDf<-data.frame(simPosLR = simParams$posLR, 
                  simNegLR = simParams$negLR, 
                  simMix = simParams$mix, 
                  fitPosLR = OLS_GraphMixRecov.ParamDf$posLR, 
                  fitNegLR = OLS_GraphMixRecov.ParamDf$negLR, 
                  fitMix = OLS_GraphMixRecov.ParamDf$mix)

CorMat_GraphMixRecov <- rcorr(as.matrix(simDf))
```

# Correlation matrix for lambda = .15, between simulated and original parameters

```{r}
cormat <- round(CorMat_GraphMixRecov$r,2)
cormat <- cormat[1:3,4:6]
library(reshape2)
melted_cormat <- melt(cormat)
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)

# Create a ggheatmap
ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 25, hjust = 1), axis.text.y = element_text( 
    size = 25) )+
 coord_fixed()

greekLab <- c(expression(alpha[p]), expression(alpha[n]), expression(phi) )

FitSimHeatMap <- ggheatmap + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_text(size=18, face="bold"),
  axis.title.y = element_text(size=18, face="bold"),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(0.48, 0.7),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5)) + xlab("Fitted") + ylab("Simulated") +
  scale_x_discrete(
        labels=greekLab)  +
  scale_y_discrete(
        labels=greekLab)
FitSimHeatMap
```

# Retaining original covariance structure: Generate behavioral data with original parameters

```{r}
x<-c('trialNum', paste0('wpe',1:148) , paste0('ws',1:148), 'RPE','V_PE', 'S_PE', 'V_S', 'Value', 'SR', 'cluster', 'prob', 'clustType', 'Idx', 'valence', 'feedback','subID')
simulated2<-as.data.frame(matrix(ncol=length(x)))
names(simulated2) <- x
simParams2 <- matrix(ncol=4)
set.seed(42)
for(i in uIds){
  
  sampParams2<-c( AsymLR.ParamDf$posLR[AsymLR.ParamDf$subID == i], AsymLR.ParamDf$negLR[AsymLR.ParamDf$subID == i], AsymLR.ParamDf$mix[AsymLR.ParamDf$subID == i] )
  curSim<-graphMixParamRecov(sampParams2, type = "in", graph = posGraph)
  subID <- i
  sampParams2<-c(sampParams2, subID)
  curSim <- cbind(curSim, subID)
  simulated2<-rbind(simulated2, curSim)
  simParams2<-rbind(simParams2, sampParams2)
}
simulated2<-simulated2[2:nrow(simulated2),1:ncol(simulated2)]
simParams2<-simParams2[2:nrow(simParams2),1:ncol(simParams2)]

simulated2<-as.data.frame(simulated2)
simParams2<-as.data.frame(simParams2)
names(simParams2) <- c("posLR","negLR","mix","subID")
```

# Fitting using original covariance structure

```{r}

  set.seed(132)
  simulated2 <- simulated2[!is.na(simulated2$SR),] # Remove missing responses; data will not fit with missing responses included
  simulated2 <- simulated2[order(simulated2$subID, simulated2$trialNum),] # Sort by trials for trial-by-trial learning
  simIds <- unique(simulated2$subID)
  x = c("simID", "posLR", "negLR", "mix", "LL", "k", "n", "BIC", "AIC")
  k = 3

    core<-detectCores()
  cl <- parallel::makeCluster(core-2, setup_strategy = "sequential")
  setDefaultCluster(cl=cl)
  registerDoParallel(cl)
  clusterExport(cl, list("cGraphMix"))
  clusterExport(cl, list("x"))
  clusterExport(cl, list("k"))
  clusterExport(cl, list("simulated2"))
  
result<-foreach(i=simIds, .combine = rbind.data.frame, .export=c('cGraphMix', 'cOptimx', 'fullDf', 'x', 'k'), .packages = c("compiler", "optimx", "scales")) %dopar% {
  paramDf <- as.data.frame(matrix(ncol = length(x)))
  names(paramDf) <- x
  subDf <- subset(simulated2, subID == i) # Subset participant data
  SSE <- function(param){ (sum((subDf$SR  - (cGraphMix(subDf$trialNum,subDf$Idx,subDf$feedback,4,posGraph,type="in",cue="single",param)$Value))^2)) } # Set objective function for SSE
  
  (output <- optimx(par = c(.04, .04, .5), method = c("L-BFGS-B"), fn = SSE, lower = c(0, 0, 0), upper = c(1,1,1))) # Set parameters for optimization
  paramDf$simID <- i
  paramDf$posLR <- output$p1
  paramDf$negLR <- output$p2
  paramDf$mix <- output$p3
  paramDf$k <- k
  paramDf$n <- nrow(subDf)
  paramDf$LL <- output$value
  paramDf$BIC <- nrow(subDf) * log(output$value/nrow(subDf)) + k * log(nrow(subDf)) # Compute BIC
  paramDf$AIC <- 2 * k + nrow(subDf) * log(output$value/nrow(subDf))
  paramDf
    
}
stopCluster(cl)
OLS_GraphMixRecov2.ParamDf <- result
```

# Plots between original and simulated (generated from original) parameters


```{r}
simParams2 <- simParams2[order(simParams2$subID),]
simDf2<-data.frame(fitPosLR = OLS_GraphMixRecov2.ParamDf$posLR, fitNegLR = OLS_GraphMixRecov2.ParamDf$negLR, fitMix = OLS_GraphMixRecov2.ParamDf$mix, 
                   #fitPosLR = AsymLR.ParamDf$posLR, fitNegLR = AsymLR.ParamDf$negLR, fitMix = AsymLR.ParamDf$mix)
                   simPosLR = simParams2$posLR, simNegLR = simParams2$negLR, simMix = simParams2$mix)

corTrueSim <- rcorr(as.matrix(simDf2))
corTrueSim

ggplot(simDf2, aes(x=simMix, y=fitMix)) + 
  geom_point()+
  geom_smooth(method=lm, colour="black") + jtools::theme_apa()

ggplot(simDf2, aes(x=simPosLR, y=fitPosLR)) + 
  geom_point()+
  geom_smooth(method=lm, colour="black") + jtools::theme_apa()

ggplot(simDf2, aes(x=simNegLR, y=fitNegLR)) + 
  geom_point()+
  geom_smooth(method=lm, colour="black") + jtools::theme_apa()
```

# Correlations between simulated (generated by original) and original

```{r}
cormat <- round(corTrueSim$r,2)
# cormat <- cormat[1:3,4:6] # I originally had it this way...
# cormat
cormat <- cormat[c(4:6),c(1:3)] # Changed it to this to pivot "Fitted" to x-axis
cormat
library(reshape2)
melted_cormat <- melt(cormat)
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

#cormat <- reorder_cormat(cormat)
upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)

# Create a ggheatmap
ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
    name="Pearson\nCorrelation") +
  theme_minimal()+ # minimal theme
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 25, hjust = 1), axis.text.y = element_text( 
    size = 25) )+
 coord_fixed()

greekLab <- c(expression(alpha[p]), expression(alpha[n]), expression(phi) )

OrigFitHeatMap <- ggheatmap + 
geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_text(size=18, face="bold"),
  axis.title.y = element_text(size=18, face="bold"),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(0.48, 0.7),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5)) + xlab("Fitted") + ylab("Original") +
  scale_x_discrete(
        labels=greekLab)  +
  scale_y_discrete(
        labels=greekLab)

OrigFitHeatMap
```

```{r}
CONFUSE <- ggpubr::ggarrange(OrigOrigHeatMap, FitSimHeatMap, OrigFitHeatMap,
          ncol = 3, nrow = 1, common.legend = T, legend = "top", labels = c("A","B","C"))


ggsave("/Volumes/Research Project/Social Evaluative Feedback fMRI/Plots/corrHeatMaps.png", units = "in", dpi = 600, width = 10, height = 4)
ggsave("/Volumes/Research Project/Social Evaluative Feedback fMRI/Plots/corrHeatMaps.tiff", units = "in", dpi = 600, width = 10, height = 4)
```

```{r}
setwd("/Volumes/GoogleDrive/My Drive/Volumes/Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/output/")
tBt_Df <- read.csv("trialBytrial.Df.csv")
se <- function(a){
  sd(a, na.rm=TRUE)/sqrt(length(na.omit(a)))
}
aggrPreds <- tBt_Df %>% mutate(truePE = abs(feedback - valEst)) %>% group_by(trialTotalT1) %>% summarise(predErrorM = mean(truePE, na.rm=T),
                                                             predErrorSD = sd(truePE, na.rm=T),
                                                             predErrorSE = se(truePE)
                                                             )

corReal = cor.test(aggrPreds$trialTotalT1, aggrPreds$predErrorM, method="spearman")
corReal

REAL_tbt <- ggplot(aggrPreds, aes(x=trialTotalT1, ymin=(predErrorM-predErrorSE), ymax=(predErrorSE+predErrorM), y=predErrorM )) +
  geom_line() +
  geom_ribbon(alpha=.25) +
  geom_smooth(method="lm",color="black",se=F) +
  xlab("Trial Number") + ylab("Average Absolute PE") + 
  jtools::theme_apa()
```

```{r}
aggrPreds <- simulated %>% mutate(truePE = abs(feedback - Value)) %>% group_by(trialNum) %>% summarise(predErrorM = mean(truePE, na.rm=T),
                                                             predErrorSD = sd(truePE, na.rm=T),
                                                             predErrorSE = se(truePE)
                                                             )

cor.test(aggrPreds$trialNum, aggrPreds$predErrorM, method="spearman")
SIMSIM_tbt <- ggplot(aggrPreds, aes(x=trialNum, ymin=(predErrorM-predErrorSE), ymax=(predErrorSE+predErrorM), y=predErrorM )) +
  geom_line() +
  geom_ribbon(alpha=.25) +
  geom_smooth(method="lm",color="black",se=F) +
  xlab("Trial Number") + ylab("Average Absolute PE") + jtools::theme_apa()
```

```{r}
aggrPreds <- simulated2 %>% mutate(truePE = abs(feedback - Value)) %>% group_by(trialNum) %>% summarise(predErrorM = mean(truePE, na.rm=T),
                                                             predErrorSD = sd(truePE, na.rm=T),
                                                             predErrorSE = se(truePE)
                                                             )

cor.test(aggrPreds$trialNum, aggrPreds$predErrorM, method="spearman")
SIMREAL_tbt <- ggplot(aggrPreds, aes(x=trialNum, ymin=(predErrorM-predErrorSE), ymax=(predErrorSE+predErrorM), y=predErrorM )) +
  geom_line() +
  geom_ribbon(alpha=.25) +
  geom_smooth(method="lm",color="black",se=F) +
  xlab("Trial Number") + ylab("Average Absolute PE") + jtools::theme_apa()
```


```{r}
ggarrange(nrow=2,ncol=1, REAL_tbt, CONFUSE)
#ggsave("/Volumes/Research Project/Social Evaluative Feedback fMRI/Plots/learnAndConfusion.png", units = "in", dpi = 600, width = 10, height = 14)
#ggsave("/Volumes/Research Project/Social Evaluative Feedback fMRI/PlotslearnAndConfusion.tiff", units = "in", dpi = 600, width = 10, height = 14)
ggsave("/Volumes/Research Project/Social Evaluative Feedback fMRI/Plots/learnAndConfusion.png", units = "in", dpi = 600, width = 7, height = 9.8)
ggsave("/Volumes/Research Project/Social Evaluative Feedback fMRI/PlotslearnAndConfusion.tiff", units = "in", dpi = 600, width = 7, height = 9.8)
```










