---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
library(readbulk)
library(MASS)
library(lme4)
library(lmerTest)
library(tidyverse)
library(ggeffects)
```

```{r}
setwd("/Volumes/GoogleDrive/My Drive/Volumes/Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/output/")
getwd()
fullDf <- read.csv("fullTDdf.csv")
tbtDf <- read.csv("trialBytrial.Df.csv")
mergedRaw <- read_bulk(directory = "/Volumes/GoogleDrive/My Drive/Volumes/Research Project/Social Evaluative Feedback fMRI/fMRI Analysis/ROI Interaction/PEs/aChangeOutT2/PCC/", extension = ".csv", fun = read.csv, header = FALSE)

tbtDf$changeScore.Z <- scale(abs(tbtDf$changeScore))
tbtDf$outDegree.Z <- scale(tbtDf$outDegree)
tbtDf$changeScoreAbs <- abs(tbtDf$changeScore)
```

load and cleaning up

```{r}
cleanDf <- mergedRaw %>% separate(File, c("subID","PE"), sep = "_aChangeOutT2_PE")
cleanDf$PE <- gsub(".csv","",cleanDf$PE)
```

changing to wide

```{r}
cleanDf <- pivot_wider(cleanDf, values_from = "V1", names_from = "PE", names_prefix = "PE.")
```


```{r}

tbtDf <- merge(tbtDf, cleanDf[c("subID","PE.1","PE.2","PE.3")], by="subID")
```

so I decided to try computing a different predicted activation that takes the subject level parameter estimates and multiplies them with the trial level outdegree and prederror variables to compute trial level predicted activation

```{r}
tbtDf$predAct = tbtDf$PE.1 * tbtDf$changeScore.Z + tbtDf$PE.2 * tbtDf$outDegree.Z + tbtDf$PE.3 * tbtDf$changeScore.Z * tbtDf$outDegree.Z
```

here is the model and plot for that

```{r}
m <- lmer(predAct ~ outDegree * changeScoreAbs + (outDegree + changeScoreAbs | subID), data = tbtDf, 
            control = lmerControl(optimizer = "bobyqa",
                                  optCtrl = list(maxfun=2e5)), REML = FALSE)
summary(m)

#ggpredict(m, terms = c("outDegree","predError")) %>% plot()
p <- ggpredict(m, terms = c("changeScoreAbs","outDegree"))
plotOUTPE<-ggplot(p, aes(x, predicted)) +  geom_line(aes(linetype=group, color=group)) + geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=group), alpha=0.15) + scale_linetype_discrete(labels = c("Low Outdegree","Mid Outdegree", "High Outdegree")) + scale_color_discrete(labels = c("Low Outdegree","Mid Outdegree", "High Outdegree")) + scale_fill_discrete( 
                      labels=c("Low Outdegree", "Mid Outdegree", "High Outdegree")) + theme(
    legend.position = c(.01, .035),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6)
    ) + theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold")) + theme(legend.text = element_text(size=20)) + theme(panel.border = element_rect(colour = "black", fill = NA, size =1)) + theme(legend.title = element_blank()) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Change Scoree") + ylab("PCC Activation")
jpeg("~/Downloads/vmPFCoutpE.jpg", units="in", width=6, height=4, res=300)
# insert ggplot code
plotOUTPE
dev.off()
```

```{r}
p <- ggpredict(m, terms = c("outDegree","changeScoreAbs[0,3,6]"))
plotOUTPE<-ggplot(p, aes(x, predicted)) +  geom_line(aes(linetype=group, color=group)) + geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=group), alpha=0.15) + scale_linetype_discrete(labels = c("Low Change","Mid Change", "High Change")) + scale_color_discrete(labels = c("Low Change","Mid Change", "High Change")) + scale_fill_discrete( 
                      labels=c("Low Change", "Mid Change", "High Change")) + theme(
    legend.position = c(.01, .6),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6)
    ) + theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold")) + theme(legend.text = element_text(size=20)) + theme(panel.border = element_rect(colour = "black", fill = NA, size =1)) + theme(legend.title = element_blank()) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Outdegree Centrality") + ylab("PCC Activation")

plotOUTPE
```


```{r}
setwd("~/Google Drive/")
tbtDf <- read.csv("./Volumes/Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/trialBytrial.Df.csv")
mergedRaw <- read_bulk(directory = "./Volumes/Research Project/Social Evaluative Feedback fMRI/fMRI Analysis/ROI Interaction/PEs/changeOutT1/changeOutvmPFC/", extension = ".csv", fun = read.csv, header = FALSE)
```

```{r}
cleanDf <- mergedRaw %>% separate(File, c("subID","PE"), sep = "_changeOutT1_PE")
cleanDf$PE <- gsub(".csv","",cleanDf$PE)
```

```{r}
tbtNeigh <- read.csv("~/Google Drive/Volumes/Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/output/tbtNeigh.csv")
distDf <- read.csv("~/Google Drive/Volumes/Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/output/distTravDf.csv")
tbtDf$noCh <- ifelse(tbtDf$changeScore == 0, 1, 0)
tbtDf$pCh <- scale(ifelse(tbtDf$changeScore > 0, tbtDf$changeScore, 0))
tbtDf$nCh <- scale(ifelse(tbtDf$changeScore < 0, tbtDf$changeScore, 0))
posCents <- read.csv("~/Google Drive/Volumes/Research Project/Trait Network_Behaviral/generating network/output/allPosCents.csv")
names(posCents)[1] <- "Trait"
tbtDf <- merge(tbtDf, tbtNeigh[c("subID","trialTotalT1","T1averageAllVE")], by = c("subID", "trialTotalT1"))
tbtDf <- merge(tbtDf, distDf[c("subID","trialTotalT1","outDist2", "outDist2cum")], by = c("subID", "trialTotalT1"))
tbtDf <- merge(tbtDf, posCents[c("Trait", "inDegree")], by = c("Trait"))
#tbtDf$valEstDist <- abs(tbtDf$valEst-tbtDf$T1averageAllVE)
```


changing to wide

```{r}
cleanDf <- pivot_wider(cleanDf, values_from = "V1", names_from = "PE", names_prefix = "PE.")
tbtDf <- merge(tbtDf, cleanDf[c("subID","PE.1","PE.2","PE.3","PE.4","PE.8")], by="subID")
```

so I decided to try computing a different predicted activation that takes the subject level parameter estimates and multiplies them with the trial level outdegree and prederror variables to compute trial level predicted activation

```{r}
test <- data.frame(noChange = tbtDf$noCh, posChange = tbtDf$pCh, negChange = tbtDf$nCh, outDegree = tbtDf$outDegree)
tbtDf$noCh <- as.numeric(tbtDf$noCh)
tbtDf$predAct = tbtDf$PE.1 * tbtDf$outDegree + tbtDf$PE.2 * tbtDf$pCh + tbtDf$PE.3 * tbtDf$nCh + tbtDf$PE.4 * tbtDf$noCh + tbtDf$PE.8 * tbtDf$outDegree * tbtDf$noCh
```


here is the model and plot for that

```{r}
tbtDf$noCh <- factor(tbtDf$noCh,
levels = c(0,1),
labels = c("Change", "Maintain"))

m2 <- lmer(predAct ~ outDegree * noCh + pCh + nCh + (outDegree + noCh + pCh + nCh  | subID), data = tbtDf, 
            control = lmerControl(optimizer = "bobyqa",
                                  optCtrl = list(maxfun=2e5)), REML = FALSE)
summary(m2)
library(ggeffects)
#ggpredict(m, terms = c("outDegree","valEstDist")) %>% plot()
p <- ggpredict(m2, terms = c("outDegree","noCh"))

plotOUTPE<-ggplot(p, aes(x, predicted)) +  geom_line(aes(linetype=group, color=group)) + geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=group), alpha=0.15) + scale_linetype_discrete(labels=c("Change","Maintain")) + scale_color_discrete(labels=c("Change","Maintain")) + scale_fill_discrete(labels=c("Change","Maintain")) + theme(
    legend.position = c(.05, .075),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6)
    ) + theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="bold")) + theme(legend.text = element_text(size=20)) + theme(panel.border = element_rect(colour = "black", fill = NA, size =1)) + theme(legend.title = element_blank()) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Outdegree Centrality") + ylab("vmPFC Activation")
plotOUTPE
jpeg("~/Downloads/vmPFC_noChangeOutdegree.jpg", units="in", width=6, height=4, res=300)
# insert ggplot code
plotOUTPE
dev.off()
```

```{r}
setwd("~/Google Drive/")
getwd()
fullDf <- read.csv("./Volumes/Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/output/fullTDdf.csv")
tbtDf <- read.csv("./Volumes/Research Project/Social Evaluative Feedback fMRI/Behavioral Data Analysis/output/trialBytrial.Df.csv")
# mergedRaw <- read_bulk(directory = "./Volumes/Research Project/Social Evaluative Feedback fMRI/fMRI Analysis/ROI Interaction/PEs/discrepOut/traitvmPFCmask/", extension = ".csv", fun = read.csv, header = FALSE)
mergedRaw <- read_bulk(directory = "./Volumes/Research Project/Social Evaluative Feedback fMRI/fMRI Analysis/ROI Interaction/PEs/discrepOut/discrepOutvmPFC/", extension = ".csv", fun = read.csv, header = FALSE)
```

load and cleaning up

```{r}
cleanDf <- mergedRaw %>% separate(File, c("subID","PE"), sep = "_discrepOut_PE")
cleanDf$PE <- gsub(".csv","",cleanDf$PE)
```

changing to wide

```{r}
cleanDf <- pivot_wider(cleanDf, values_from = "V1", names_from = "PE", names_prefix = "PE.")
```

okay, so then I tried merging the average predicted activation per subject with the multilevel dataframe with level 1 units for prederror and outdegree. it still turns out weird

```{r}

tbtDf <- merge(tbtDf, cleanDf[c("subID","PE.1","PE.2","PE.3")], by="subID")
```

so I decided to try computing a different predicted activation that takes the subject level parameter estimates and multiplies them with the trial level outdegree and prederror variables to compute trial level predicted activation

```{r}
data.frame(tbtDf$PE.1, scale(tbtDf$feedback), tbtDf$PE.2, scale(tbtDf$outDegree), tbtDf$PE.3, scale(tbtDf$outDegree), scale(tbtDf$feedback))

tbtDf$predAct = tbtDf$PE.1 * scale(tbtDf$feedback) + tbtDf$PE.2 * scale(tbtDf$outDegree) + tbtDf$PE.3 * scale(tbtDf$outDegree) * scale(tbtDf$feedback)
```

here is the model and plot for that

```{r}
m <- lmer(predAct ~ outDegree * feedback + (outDegree + feedback | subID), data = tbtDf, 
            control = lmerControl(optimizer = "bobyqa",
                                  optCtrl = list(maxfun=2e5)), REML = FALSE)
summary(m)

```
```{r}
#ggpredict(m, terms = c("outDegree","predError")) %>% plot()
p <- ggpredict(m, terms = c("outDegree","feedback[1,4,7]"))
plotOUTPEVMPFC<-ggplot(p, aes(x, predicted)) +  geom_line(aes(linetype=group, color=group)) + geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=group), alpha=0.15) + scale_linetype_discrete(labels = c("Negative Feedback","Moderate Feedback", "Positive Feedback")) + scale_color_discrete(labels = c("Negative Feedback","Moderate Feedback", "Positive Feedback")) + scale_fill_discrete( 
                      labels=c("Negative Feedback","Moderate Feedback", "Positive Feedback")) + theme(
    legend.position = c(.01, .7),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6)
    ) + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) + theme(legend.text = element_text(size=12)) + theme(panel.border = element_rect(colour = "black", fill = NA, size =1)) + theme(legend.title = element_blank()) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Outdegree Centrality") + ylab("vmPFC Parameter Estimate")
# jpeg("~/Documents/UC Riverside/Studies/fMRI Feedback/Manuscript/Figures/vmPFCoutFeed.jpg", units="in", width=6, height=4, res=300)
# insert ggplot code
plotOUTPEVMPFC
# dev.off()

ggsave(plot = plotOUTPEVMPFC, filename = "~/Documents/UC Riverside/Studies/fMRI Feedback/Manuscript/Figures/vmPFCoutFeed.jpg", dpi = 600, units="in", height = 7, width = 4)
```

```{r}
comb <- ggpubr::ggarrange(plotOUTPE, plotOUTPEVMPFC)
ggsave(plot=comb, filename="~/Documents/UC Riverside/Studies/fMRI Feedback/Manuscript/Figures/outcomb.jpg", dpi=600, units="in", width=10, height = 4)
```

